\speculake: Hiding Malware in Speculative Execution

### 2018-12-10 paper/implementation.tex
Included multi-indexing in bandwidth section

% TODO: this could move elsewhere?
We demonstrate the speed that information can be decrypted via the speculative
world, and we vary the channel width of the side channel from 1 to 12 bits to
measure its performance. At low channel width, reading from the cache side
channel requires timing reads from only 2 locations, while at 12-bits, the side
channel requires reading $2^{12}$ locations. On the other hand, there is a fixed
overhead per speculative iteration that favors increased channel width to
maximize bandwidth. As shown in Figure~\ref{fig:spec_bandwidth}, 8 bits is the
optimal side channel width, allowing us to decrypt over 5,000 bits per second
(625 Bytes/sec).
% Iterations: 20

>>>>

% TODO: this could move elsewhere?
We demonstrate the speed that information can be decrypted via the speculative
world, and we vary the channel width of the side channel from 1 to 12 bits to
measure its performance. At low channel width, reading from the cache side
channel requires timing reads from only 2 locations, while at 12-bits, the side
channel requires reading $2^{12}$ locations. On the other hand, there is a fixed
overhead per speculative iteration that favors increased channel width to
maximize bandwidth. As shown in Figure~\ref{fig:spec_bandwidth}, 8 bits is the
optimal side channel width, allowing us to decrypt over 5,000 bits per second
(625 Bytes/sec). We have managed to improve upon this number by loading multiple 
values into the probe array in any given round. For example, a probe array 
of size 1024 can be split into four sections of 256 bits, each with their 
own index -- providing a 32 bit channel overall. The drawback of this 
method is that loading these values into the probe array is a non-zero 
exspense on the limited $\mu$~operation budget. We have successfully 
implemented a decrypt gadget that passes 32 bits per round using four indices 
into a 1024 bit probe array, which is able to decrypt over 11,000 bits per second 
(1,425 Bytes/sec).

% Iterations: 20
